%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[12pt]{article}
\usepackage[margin=0.6in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{moresize}
\usepackage{lipsum}
\usepackage{nopageno}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{multicol}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Hoefler Text}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Lato}
\setmonofont[Scale=MatchLowercase]{Roboto Mono}

\newcommand{\sqsep}{\quad {\tiny $\blacksquare$} \quad}
\newcommand{\gap}{\hspace*{1em}}

\setlist[itemize]{leftmargin=2.2cm, itemsep=0cm}
\newlist{explist}{itemize}{4}
\setlist[explist,1]{label=\textbullet,leftmargin=2.2cm}
\setlist[explist,2]{label=$\mathbin{\vcenter{\hbox{\rule{0.5ex}{0.5ex}}}}
$,leftmargin=0.5cm,topsep=-0.2cm,itemsep=-0.2cm}
\setlist[explist,3]{label=\!, leftmargin=0.4cm, topsep=-0.25cm, itemsep=-0.2cm}
\setlist[explist,4]{label=\!, leftmargin=0.4cm, topsep=-0.25cm}

\begin{document}

\begin{center}
	{\HUGE \textbf{Zac Garby}}
	
	me@zacgarby.co.uk \sqsep
	zac.garby@nottingham.ac.uk \sqsep
	%07737 132131 \sqsep  % UNCOMMENT FOR REAL CV
	zacgarby.co.uk
\end{center}

% UNCOMMENT THESE LINES FOR REAL CV
%\begin{table}[h]
%\begin{center}
%\begin{tabularx}{\textwidth}{X r r}
%& Studio C26 \\
%& 15 Freckingham Street \\
%& Nottingham \\
%& NG1 1DQ \\
%\end{tabularx}
%\end{center}
%\end{table}
% \vspace{-5em} % UNCOMMENT THIS LINE FOR REAL CV
% \vspace{-1em} % COMMENT THIS LINE FOR REAL CV

\section*{Experience \& Volunteering}

\begin{explist}
	\item[2023-present] \textit{University of Nottingham,} PhD Student
	{\small \begin{explist}
		\item A member of the Functional Programming Lab under supervision of Professor Graham Hutton.
		\item I am working on compiler calculation methods, with a particular focus on languages with effects.
	\end{explist}}
	\item[2022-2023] \textit{HackSoc Nottingham,} President
	{\small \begin{explist}
		\item I was responsible for the society, including the community itself and its reputation, but also organisation and planning. I gave many talks and workshops, and retained my Graphics Officer duties.
	\end{explist}}
	\item[2021-2023] \textit{HackSoc Nottingham,} Lead organiser, HackNotts
	{\small \begin{explist}
		\item I was responsible for the general planning and logistics of the event, as well as communicating with various companies to arrange funding and grants.
		\item HackNotts 23 was the largest HackNotts ever, with 204 attendees in total.
	\end{explist}}
	\item[2021-2022] \textit{HackSoc Nottingham,} Development Secretary and Graphics Officer.
	{\small \begin{explist}
		\item I gave a number of workshops and talks on tech-related topics each month.
		\item I maintained the society's website, graphics, and infrastructure.
	\end{explist}}
	\item[2020-2021] \textit{University of Nottingham,} A Computer Science mentor.
	{\small \begin{explist}
		\item I was assigned to a small group of first-year students to help them settle in to University.
		\item I ran a number of sessions with my group to help them with their first-year modules.
	\end{explist}}
	\item[2018] \textit{National Citizen Service}, Participant.
	{\small \begin{explist}
		\item As part of a team, raised money and restored a youth centre in Dorchester.
	\end{explist}}
	\item[2017-2019] \textit{Thomas Hardye School,} Ran the Programming \& Robotics club.
	{\small \begin{explist}
		\item Taught a group of Year 9 and GCSE students about programming, mainly through the context of robotics.
	\end{explist}}
	\item[2017-2019] \textit{Thomas Hardye School,} Volunteered at a number of STEM days.
	{\small \begin{explist}
		\item Ran half-day sessions teaching middle school students about programming and simple robotics using LEGO Mindstorm.
	\end{explist}}
\end{explist}

\section*{Education}

\begin{explist}
	\item[2019-2023] \textbf{University of Nottingham} \\
		  MSci Computer Science
		  {\small
		  \begin{explist}
		  	\item[] First Class with Honours (87\% average, awarded the best overall performance prize).
			\item[] Highest ever grade in Computer Science at the University of Nottingham.
		  \end{explist}
		  }
		  
	\item[2015-2019] \textbf{The Thomas Hardye School, Dorchester } \\
		A-Levels
		{\small
		\begin{explist}
			\item[] Mathematics, Further Mathematics, Computer Science, and Physics: \textit{A*AAA}
		\end{explist}
		}
\end{explist}

\section*{Skills \& Interests}
\begin{itemize}
	\item Extensive experience in Haskell, Python, C, Go, JavaScript, Agda, Java, and \LaTeX. Also some experience with Rust, various LISPs, and numerous domains specific languages.
	\item As the ex-President of \textit{HackSoc} at the University of Nottingham, I am an experienced public speaker, and can confidently take on leadership positions. Having led the organisation of \textit{HackNotts}, I am comfortable communicating with organisations, dealing with finance, and sorting out logistics and large-scale plans.
	\item Strong interest in many areas related to programming language theory, including type theory, compiler design/implementation, and interactivity in programming languages.
	\item Varied experience with many areas of programming and computer science, including multimedia (image processing, audio processing/synthesis, game development), systems programming, scientific computing, full-stack web development, networking, and the design and implementation of programming language compilers.
	\item Strong interest in hackathons, both as an attendee and as an organiser. I've attended 15 hackathons and organised two of them. A complete portfolio is available on my website.
	\item Interested in mathematics, especially where it overlaps with Computer Science.
	\item I enjoy playing, listening to, and creating music; I play the guitar and the piano, but I am really interested in early music and am currently building a lute. I also enjoy reading, climbing, bouldering, and I am a member of---and a Training Officer at---the University of Nottingham's Medieval Combat Society.
	\item I have an Emergency First Aid at Work qualification.
\end{itemize}

\section*{Awards, Achievements, \& Honours}
\begin{itemize}
	\item[2024] \textit{AstonHack 9,} Second place prize for my project, ``Lunatic Lander'', a mixed-reality hardware game simulating a moon landing on a rotating model of the moon.
	\item[2024] \textit{HackSussex 2024,} First place prize for my project, ``Scribble Scraps'', a game where real-life objects are turned into digital creatures using computer vision.
	\item[2024] \textit{Royal Hackaway v7,} First place prize for my project, ``Jailbreak'', a game exploring a dystopian future where prisons are controlled by artificial intelligence.
	\item[2023] \textit{University of Nottingham,} Elizabeth and J D Marsden Prize, 3rd place. Awarded to ``the best students of the year'' for academic performance and ``outstanding character and personality''.
	\item[2023] \textit{Computer Science, University of Nottingham,} Outstanding Community Contribution Prize, for my work organising HackNotts '21 and '23.
	\item[2023] \textit{Computer Science, University of Nottingham,} Best Overall Performance Prize, for achieving the highest overall (over the full four years) grade percentage in my cohort.
	\item[2023] \textit{Computer Science, University of Nottingham,} Best Year 4 Research Project Prize, for my work on the \textit{Fantasia} program synthesis engine.
	\item[2023] \textit{Computer Science, University of Nottingham,} High Achiever's Award, for being within the top 5\% in my year in terms of grades.
	\item[2023] \textit{SussexHack 23,} Second place prize for my project, ``Knuckles'', a biomechanical robot hand using shape-memory alloys.
	\item[2022] \textit{OxfordHack 22,} Won the \textit{``What the Hack?!''} prize for my project, ``MusicBoard'', a novel pen-and-paper musical instrument.
	\item[2022] \textit{Computer Science, University of Nottingham,} Best Individual Year 3 Dissertation prize for my work on the \textit{Fugue} programming language.
	\item[2022] \textit{Computer Science, University of Nottingham,} High Achiever's Award, for being within the top 5\% in my year in terms of grades.
	\item[2021] \textit{AstonHack 2021,} First place for my project, ``Network over Rube Goldberg Machine'', an experiment in physical data transmission.
	\item[2021] \textit{AstonHack 2021,} The ``Communication Prize'', a sponsor prize, also for my project, ``Network over Rube Goldberg Machine''.
	\item[2021] \textit{Computer Science, University of Nottingham,} High Achiever's Award, for being within the top 5\% in my year in terms of grades.
	\item[2020] \textit{HackNotts 2020,} Sponsored prize for my project, ``The Haskelltron 2000'', a Haskell interpreter embedded in a standard receipt printer.
	\item[2020] \textit{Computer Science, University of Nottingham,} High Achiever's Award, for being within the top 5\% in my year in terms of grades.
	\item[2019] \textit{Computer Science, University of Nottingham,} Silver Scholarship (a 25\% tuition fee rebate each of my four years at university).
	\item[2019] \textit{Thomas Hardye School,} Selected by my school to create an interactive exhibit for the local community's ``50th Anniversary of the Moon Landing'' event.
	\item[2019] \textit{Thomas Hardye School,} Received my school's first ever Computer Science subject award.
	\item[2018] \textit{United Kingdom Mathematics Trust,} Silver award in the Senior Mathematical Challenge.
	\item[2015] \textit{Bournemouth University,} Second place out of hundreds of entries in a programming competition.
\end{itemize}

\section*{References}
Available upon request.

\vfill

\end{document}  