%-------------------------
% Resume in Latex
% Author : Zac Garby
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tgbonum}

\input{glyphtounicode}

\fontfamily{phv}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge\scshape Zac Garby} \\ \vspace{10pt}
    \textbf{\large\scshape zacgarby.co.uk} \\ \vspace{10pt}
    07737 132 131 $|$
    \href{mailto:me@zacgarby.co.uk}{me@zacgarby.co.uk} $|$
    \href{mailto:psyzg5@nottingham.ac.uk}{psyzg5@nottingham.ac.uk} $|$
    \href{https://github.com/zac-garby}{github.com/zac-garby}
\end{center}

A second year Computer Science student at the University of Nottingham. Interested especially in functional programming, type theory, and compilers/programming language design.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Nottingham}{Nottingham, England}
      {MSci Computer Science. 90\% first-year average.}{September 2019 -}
      \resumeItemListStart
        \resumeItem{Used multiple languages including Haskell, C, and Java.}
        \resumeItem{Experience with web development, databases, and software engineering practices.}
      \resumeItemListEnd
    \resumeSubheading
      {The Thomas Hardye School}{Dorchester, England}
      {A Levels in Maths (A*), Further Maths (A), Computer Science (A), and Physics (A)}{September 2014 - July 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Beachside Fish \& Chips}{Weymouth, England}
      {Retail Worker}{July-August 2018}
      \resumeItemListStart
        \resumeItem{Part time work during the summer holidays.}
        \resumeItem{Experience dealing with dozens of customers at a time at the peak of the tourist season.}
        \resumeItem{Handling payments, restocking shelves, and coordinating timing with coworkers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ZZZZ} $|$ \emph{Haskell, \texttt{ReadP} Parser Combinators} $|$ \textbf{github.com/zac-garby/zzzz}}{}
          \resumeItemListStart
            \resumeItem{Developed a lazily-evaluated Lisp-based programming language from scratch.}
            \resumeItem{Similar paradigm to Haskell, giving me a better understanding of its internals.}
            \resumeItem{Gave me a lot of experience in working with large Haskell codebases.}
            \resumeItem{Created a GitHub pages website to demonstrate the language.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{iTunes Graphs} $|$ \emph{Swift, UIKit, Cocoa, Objective-C iTunes Library} $|$ \textbf{github.com/zac-garby/iTunes-Graphs}}{}
          \resumeItemListStart
            \resumeItem{Developed an iOS and a macOS app to gather data about the user's iTunes music library and give graphical insights.}
            \resumeItem{46 stars (combined) on GitHub, was included in the ``Awesome Mac'' software list.}
            \resumeItem{Experience with user interface design, for desktop computers and mobile devices.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Computer} $|$ \emph{Logisim, Kicad, Machine Code, Assembly, Python} $|$ \textbf{github.com/zac-garby/computer}}{}
          \resumeItemListStart
            \resumeItem{Developed a CPU from scratch at the logic gate level, along with a custom instruction set.}
            \resumeItem{Created a parser and compiler for an assembly language in Python.}
            \resumeItem{Designed and virtually tested an electronic circuit for the computer (I never built it in real life due to cost problems.)}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Solar System} $|$ \emph{C++, SFML, Travis CI} $|$ \textbf{github.com/zac-garby/solar-system}}{}
          \resumeItemListStart
            \resumeItem{Developed a 2D game, randomly generates a ``solar system'' and simulates interactions and diplomacy between planets.}
            \resumeItem{Received and handled contributions from 12 other people via git and GitHub.}
            \resumeItem{Set up a continuous integration system with Travis CI to streamline the contribution process.}
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Haskell, Go, Rust, C, C++, C\#, Python, JavaScript, HTML/CSS, PHP, LaTeX, Common Lisp, ARM Assembly, SQL, Bash/Zsh, Swift, Agda, Java, and Lua.} \\
     \textbf{Frameworks}{: Tensorflow/Keras, React, Node.js, Vue, Hakyll, LWJGL, and Unity.} \\
     \textbf{Developer Tools}{: Git, GitHub, TravisCI, Amazon Web Services, VS Code, TextMate, Eclipse, and Emacs.} \\
     \textbf{Libraries}{: Parsec, LibGDX, LWJGL, OpenGL, SFML, SDL, WebAudioAPI, WebSockets, NumPy, Matplotlib.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
